Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-10 ms.tex
cleaned up

We adopt halo average star formation rates measured in cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any spatial variation in the star formation rate for any given galaxy. Galaxies of mass $\gsim 7\times 10^{10} \Msun$, assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, such that for a given halo mass the galactic nucleus may be older than in our model and thus more prone to thermal instability.  On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law.  They note that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards galactic centre {\bf AG mass
        threshold for this effect}.

      In fact it is possible that the mass injection is dominated by a
      nuclear star cluster with a break radius on parsec
      scales, i.e. much smaller than our fiducial break
      radius of $r_b \sim 100$ pc. If the heating is sufficiently high moving the
      break radius inwards would merely change the outer gas density
      profile, without changing the stagnation radius in the flow and
      thus the accretion rate onto the black hole. Of course if one
      moves the break radius inside where the stagnation radius would
      be for large break radii, the stagnation radius would move
      inwards somewhat. However note the for high heating rate ($v_w
      \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
      \Msun$), we predict stagnation radii smaller than a parsec.

>>>>

We adopt halo average star formation rates measured in cosmological simulations by \citet{MosterNaab+:2013a}, and neglect any spatial variation in the star formation rate for any given galaxy. Galaxies of mass $\gsim 7\times 10^{10} \Msun$, assemble their stars from the inside out \citep{PerezCidFernandes+:2013a}, such that for a given halo mass the galactic nucleus may be older than in our model and thus more prone to thermal instability.

On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law.  They note that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards galactic centre {\bf AG mass
        threshold for this effect}.

      It is thus possible that the mass injection to the nucleus could in some cases be dominated by a nuclear star cluster with its own break radius on parsec scales, i.e. much smaller than our fiducial value of $r_b \sim 100$ pc.  For a sufficiently high heating rate, a smaller break radius would not appreciably change the stagnation radius, resulting in a similar accretion rate onto the black hole.  On the other hand, a break radius smaller than the nominal stagnation radius would likely decrease the stagation radius and SMBH accretion rate.  
%      be for large break radii, the stagnation radius would move
 %     inwards somewhat. However note the for high heating rate ($v_w
  %    \gsim 500 $ km/s and small black hole masses $\Mbh \lsim 10^7
   %   \Msun$), we predict stagnation radii smaller than a parsec.
